Results

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added comment
added word

To investigate the ecological validity of the subjective values of ER strategies we calculated, we tested whether SVs were associated with the actual choice of participants in the choice block.
Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVChoice)).

@@

We then conducted a ordinal regression with the dependent variable "choice" and the individual SVs of all three strategies as independent variables.
Overall model fit was fair with $R^{2}=$ `r papaja::printnum(Choice_OrdReg_R2)`.
The predictor SV of strategy distraction was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$distraction_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[2,2])`).
The estimated odds ratio indicated a higher chance of choosing strategy distraction, when SV of that strategy is higher.
Additionally, the predictor SV of strategy suppression was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$suppression_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[4,3])`).
The estimated odds ration indicated that is more likely to later choose suppression, when SV of strategy suppression is higher.

>>>>

To investigate the ecological validity of the subjective values of ER strategies we calculated, we tested whether SVs were associated with the actual choice of participants in the choice block.
Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVChoice)). <!--JZ: Vielleicht wäre hier eine Heatmap auch ganz nice, das scheint wohl eine gute Visualisierung für einen Chi Square Test zu sein (https://www.analyticsvidhya.com/blog/2021/06/decoding-the-chi-square-test%E2%80%8A-%E2%80%8Ause-along-with-implementation-and-visualization/)-->

@@

We then conducted an ordinal regression with the dependent variable "choice" and the individual SVs of all three strategies as independent variables.
Overall model fit was fair with $R^{2}=$ `r papaja::printnum(Choice_OrdReg_R2)`.
The predictor SV of strategy distraction was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$distraction_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[2,2])`).
The estimated odds ratio indicated a higher chance of choosing strategy distraction, when SV of that strategy is higher.
Additionally, the predictor SV of strategy suppression was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$suppression_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[4,3])`).
The estimated odds ration indicated that a participant is more likely to later choose suppression, when SV of strategy suppression is higher.
